Drawing Math

### 2022-09-25 paper/Paper.tex
change frontend endpoint
mainnet deploy

Naturally, the authors were curious whether a Turtle in ``3D" would also draw 
interesting paths. In other words, what if the turtle's orientation was described
by 2 angles, pitch and yaw. The pitch and yaw would then by independently updated
by 2 decimal sequences generated from 2 rational numbers.
% TODO: figure
\begin{figure}[h!]
  \centering
  \includegraphics[width=8cm]{fig/turtle.png}
  \caption{The above is a placeholder, I would like to get Shiva to help me design a 3D graphic here similar to Figure 1 but in 3D}
\end{figure}
After writing the program, we noticed that the turtle would often fail
to close. In other words, the turtle would go off in one direction forever.
% TODO: picture of failing to close in 3d space
But, the turtle \textit{sometimes} closed.
\begin{figure}[h!]
  \centering
  \includegraphics[width=8cm]{fig/failclose3d.png}
  \caption{A non closing 3D shape generated from $\frac{102}{999} = 0.\overline{102}$ and $\frac{223}{999} = 0.\overline{223}$ in base 10.}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=8cm]{fig/tempclose.jpeg}
  \caption{A closing 3D shape generate from (?????... this is a placeholder).}
\end{figure}

@@

\pagebreak
\section{Open Questions and Future Work}
A whole host of questions naturally arise from this problem. We will proceed to list
the ones which immediately stand out. For a complete list of open problems, which have
been solved, and the associated (financial) reward to each question, see our website
\begin{enumerate}
  \item \textbf{Periodic Digit Sum in NP?}: As far as the authors are aware, given 
  any rational number, $\frac{n}{d}$ in a fixed base $b$, is finding the sum of the digits in
  one period modulo $b$ in $NP$? I.e. could one give a poly-size
  certificate to a poly-time verifier which verifies if a digital sum equals $\sigma \in \Z_b$?
  The size of the input is the number of bits required to describe $\frac{n}{d}$. The authors 
  feel that intuitively the answer should be yes. A certificate could potentially be related
  to the prime factors of the denominator and the period length. I.e.\ we know how to find
  the periodic digital sum of a prime in polynomial time (see \ref{remark:digsum-complexity}). So,
  could we somehow use this in combination with a prime factorization?

>>>>

Naturally, the authors were curious whether a Turtle in ``3D" would also draw 
interesting paths. In other words, what if the turtle's orientation was described
by 2 angles, pitch and yaw. The pitch and yaw would then by independently updated
by 2 decimal sequences generated from 2 rational numbers.
% TODO: figure
\begin{figure}[h!]
  \centering
  \includegraphics[width=8cm]{fig/turtle3dtimestep.png}
  \caption{An example of a turtle updating its rotational direction.}
\end{figure}
After writing the program, we noticed that the turtle would often fail
to close. In other words, the turtle would go off in one direction forever.
But, the turtle \textit{sometimes} closed.
\begin{figure}[h!]
  \centering
  \includegraphics[width=8cm]{fig/failclose3d.png}
  \caption{A non closing 3D shape generated from $\frac{7}{11} = 0.\overline{63}$ and $\frac{10}{11} = 0.\overline{90}$ in base 10.}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=8cm]{fig/tempclose.jpeg}
  \caption{A closing 3D shape generate from $\frac{7}{13}$ and $\frac{2}{3}$ in base $10$.}
\end{figure}

@@

\pagebreak
\section{Finding Duplicates}
- TODO: proof of comp
- difficulty of otherwise

\section{Open Questions and Future Work}
A whole host of questions naturally arise from this problem. We will proceed to list
the ones which immediately stand out. For a complete list of open problems, which have
been solved, and the associated (financial) reward to each question, see our website
\begin{enumerate}
  \item \textbf{Periodic Digit Sum in NP?}: As far as the authors are aware, given 
  any rational number, $\frac{n}{d}$ in a fixed base $b$, is finding the sum of the digits in
  one period modulo $b$ in $NP$? I.e. could one give a poly-size
  certificate to a poly-time verifier which verifies if a digital sum equals $\sigma \in \Z_b$?
  The size of the input is the number of bits required to describe $\frac{n}{d}$. The authors 
  feel that intuitively the answer should be yes. A certificate could potentially be related
  to the prime factors of the denominator and the period length. I.e.\ we know how to find
  the periodic digital sum of a prime in polynomial time (see \ref{remark:digsum-complexity}). So,
  could we somehow use this in combination with a prime factorization?
